Program Transformations for miniKanren

### 2020-08-25 papers/miniKanren/slides/evalUnfold.tex
Slides reworked to have a single running example

\begin{tikzpicture}[
  processTree,
  anchor=center,
  level 2/.style={level distance=5em},
  level 3/.style={level distance=4em},
  sibling distance=10em]
  \node (root) {\rel{eval}{$fm \ s \ true$}}
      child { node {
        \rel{and}{$a \ b \ true$} \and
        \rel{eval}{$x \ s \ a$} \and
        \rel{eval}{$y \ s \ b$} \\
        \subst{$fm \to conj \ x \ y$}}
        child { node (d) [diamond] {\and}
          child { node {\rel{and}{$a \ b \ true$}}
            child { node (subst) {\subst{$b \to true, a \to true$}}}}
          child { node (x) {\rel{eval}{$x \ s \ a$}}
          child { node[draw=none, fill=none] {...}}
          }
          child { node (y) {\rel{eval}{$y \ s \ b$}}
            child { node[draw=none, fill=none] {...}}
        }
      }
    }
    ;

@@

  \node[right=4em of root, yshift=-0.5cm] (lookup) {...};
  \draw [->] (root.east) to [in=170,out=-10] (lookup.west);

  \draw [red,<->] ($(subst.south)+(0.5,0.15)$) to [out=300,in=-100] node[below, draw=none, red] {\Large data lost} ($(x.south)+(0.85,0.15)$);

  \draw [red,<->] ($(subst.south)+(-1.2,0.15)$) to [out=300,in=240] node[below, draw=none, red] {\Large data lost} ($(y.south)+(0.8,0.15)$);

  \draw [densely dotted,->] ($(d.east)+(5,0.5)$) node[above,draw=none] {\Large split node} to [out=210,in=0] (d.east);
\end{tikzpicture}

>>>>

\begin{tikzpicture}[
  processTree,
  anchor=center]
  \node (root) {\rel{eval}{$fm \ s \ true$}}
    child { node {$fm \equiv conj \ x \ y $ \and \rel{and}{$a \ b \ true$} \and \rel{eval}{$x \ s \ a$} \and \rel{eval}{$y \ s \ b$}}
      child { node {
        \rel{and}{$a \ b \ true$} \and
        \rel{eval}{$x \ s \ a$} \and
        \rel{eval}{$y \ s \ b$} \\
        \subst{$fm \to conj \ x \ y$}}
    }
    }
    ;

@@

  \node[right=4em of root, yshift=-0.5cm] (lookup) {...};
  \draw [->] (root.east) to [in=170,out=-10] (lookup.west);
\end{tikzpicture}

### 2020-08-25 papers/miniKanren/slides/propCPDNoSplit.tex
Slides reworked to have a single running example

\begin{tikzpicture}[
  processTree,
  anchor=center,
  level 2/.style={level distance=5em},
  level 3/.style={level distance=4em},
  sibling distance=10em]
  \node (root) {\rel{eval}{$fm \ s \ true$}}
      child { node {
        \rel{and}{$a \ b \ true$} \and
        \rel{eval}{$x \ s \ a$} \and
        \rel{eval}{$y \ s \ b$} \\
        \subst{$fm \to conj \ x \ y$}}
        child { node (d) [diamond] {\and}
          child { node {\rel{and}{$a \ b \ true$}}
            child { node (subst) {\subst{$b \to true, a \to true$}}}}
          child { node (x) {\rel{eval}{$x \ s \ a$}}
          child { node[draw=none, fill=none] {...}}
          }
          child { node (y) {\rel{eval}{$y \ s \ b$}}
            child { node[draw=none, fill=none] {...}}
        }
      }
    }
    ;

@@

  \draw [red,<->] ($(subst.south)+(0.5,0.15)$) to [out=300,in=-100] node[below, draw=none, red] {\Large data lost} ($(x.south)+(0.85,0.15)$);

  \draw [red,<->] ($(subst.south)+(-1.2,0.15)$) to [out=300,in=240] node[below, draw=none, red] {\Large data lost} ($(y.south)+(0.8,0.15)$);

  \draw [densely dotted,->] ($(d.east)+(5,0.5)$) node[above,draw=none] {\Large split node} to [out=210,in=0] (d.east);
\end{tikzpicture}

>>>>

\begin{tikzpicture}[
  processTree,
  anchor=center,
  level 2/.style={level distance=5em},
  level 3/.style={level distance=4em},
  sibling distance=10em]
  \node (root) {\rel{eval}{$fm \ s \ true$}}
      child { node {
        \underline{\rel{and}{$a \ b \ true$}} \and
        \rel{eval}{$x \ s \ a$} \and
        \rel{eval}{$y \ s \ b$} \\
        \subst{$fm \to conj \ x \ y$}}
        child { node {
          \underline{\rel{eval}{$x \ s \ true$}} \and
          \rel{eval}{$y \ s \ true$} \\
          \subst{$a \to true, b \to true$}}
          child {node {
            \underline{\rel{and}{$x' \ y' \ true$}} \and
            \rel{eval}{$x' \ s \ a'$} \and
            \rel{eval}{$y' \ s \ b'$} \and
            \rel{eval}{$y \ s \ b$} \\
            \subst{$x \to conj \ x' \ y'$}
          }
          child { node (grow) {
            \underline{\rel{eval}{$x' \ s \ a'$}} \and
            \rel{eval}{$y' \ s \ b'$} \and
            \rel{eval}{$y \ s \ b$} \\
            \subst{$a' \to true, b' \to true$}}
            child {node[draw=none,fill=none] {...}}
          }
        }
      }}
    ;

@@

  \draw [red,->] ($(grow.east)+(1,-2.5)$) node[below,draw=none,anchor=north east] {\Large uncontrollable growth} to [out=45,in=0] (grow.east);

\end{tikzpicture}

### 2020-08-25 papers/miniKanren/slides/propCPDShort.tex
Slides reworked to have a single running example

\begin{tikzpicture}[
  processTree,
  anchor=center,
  level 2/.style={level distance=5em},
  level 3/.style={level distance=4em},
  sibling distance=10em]
  \node (root) {\rel{eval}{$fm \ s \ true$}}
      child { node {
        \underline{\rel{and}{$a \ b \ true$}} \and
        \rel{eval}{$x \ s \ a$} \and
        \rel{eval}{$y \ s \ b$} \\
        \subst{$fm \to conj \ x \ y$}}
        child { node {
          \underline{\rel{eval}{$x \ s \ true$}} \and
          \rel{eval}{$y \ s \ true$} \\
          \subst{$a \to true, b \to true$}}
          child {node {
            \underline{\rel{and}{$x' \ y' \ true$}} \and
            \rel{eval}{$x' \ s \ a'$} \and
            \rel{eval}{$y' \ s \ b'$} \and
            \rel{eval}{$y \ s \ b$} \\
            \subst{$x \to conj \ x' \ y'$}
          }
          child { node (grow) {
            \underline{\rel{eval}{$x' \ s \ a'$}} \and
            \rel{eval}{$y' \ s \ b'$} \and
            \rel{eval}{$y \ s \ b$} \\
            \subst{$a' \to true, b' \to true$}}
            child {node[draw=none,fill=none] {...}}
          }
        }
      }}
    ;

@@

  \draw [red,->] ($(grow.east)+(1,-2.5)$) node[below,draw=none,anchor=north east] {\Large uncontrollable growth} to [out=45,in=0] (grow.east);

>>>>

\begin{tikzpicture}[
  processTree,
  anchor=center,
  level 2/.style={level distance=5em},
  level 3/.style={level distance=4em},
  sibling distance=10em]
  \node (root) {\rel{eval}{$fm \ s \ true$}}
      child { node {
        \underline{\rel{and}{$a \ b \ true$}} \and
        \rel{eval}{$x \ s \ a$} \and
        \rel{eval}{$y \ s \ b$} \\
        \subst{$fm \to conj \ x \ y$}}
        child { node {
          \underline{\rel{eval}{$x \ s \ true$}} \and
          \rel{eval}{$y \ s \ true$} \\
          \subst{$a \to true, b \to true$}}
          child {node[draw=none,fill=none] {...}}
        }
      }
    ;

@@

### 2020-08-25 papers/miniKanren/slides/propCPDSplit.tex
Slides reworked to have a single running example

\begin{tikzpicture}[
  processTree,
  anchor=center,
  level 2/.style={level distance=5em},
  level 3/.style={level distance=4em},
  sibling distance=10em]
  \node (root) {\rel{eval}{$fm \ s \ true$}}
      child { node {
        \underline{\rel{and}{$a \ b \ true$}} \and
        \rel{eval}{$x \ s \ a$} \and
        \rel{eval}{$y \ s \ b$} \\
        \subst{$fm \to conj \ x \ y$}}
        child { node {
          \underline{\rel{eval}{$x \ s \ true$}} \and
          \rel{eval}{$y \ s \ true$} \\
          \subst{$a \to true, b \to true$}}
          child {node[draw=none,fill=none] {...}}
        }
      }
    ;

@@

>>>>

\begin{tikzpicture}[
  processTree,
  anchor=center,
  level 2/.style={level distance=5em},
  level 3/.style={level distance=4em},
  level 4/.style={level distance=3em},
  sibling distance=10em]
  \node (root) {\rel{eval}{$fm \ s \ true$}}
      child { node {
        \underline{\rel{and}{$a \ b \ true$}} \and
        \rel{eval}{$x \ s \ a$} \and
        \rel{eval}{$y \ s \ b$} \\
        \subst{$fm \to conj \ x \ y$}}
        child { node {
          \rel{eval}{$x \ s \ true$} \and
          \rel{eval}{$y \ s \ true$} \\
          \subst{$a \to true, b \to true$}}
          child { node [diamond] {\and}
            child { node (x) {
              \rel{eval}{$x \ s \ true$}}
            }
            child { node (y) {
              \rel{eval}{$y \ s \ true$}}}
          }
        }
      }
    ;

@@

  \draw[dashed,->] (x.west) to [out=165,in=-165] (root.west);
  \draw[dashed,->] (y.east) to [out=15,in=-15] (root.east);
